\documentclass{two-column-resume}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{top=1cm, left=1cm, right=1cm}

\begin{document}
\name{Zhihao (Johnson)}{Du}
\contact{\href{mailto:zhihao617@berkeley.edu}{zhihao617@berkeley.edu} | +1 (510) 833-4417}
\headerline
\noindent
\begin{minipage}[t]{0.23\textwidth}
    \vspace{0.25\baselineskip}
    \section{Links}
        \shortitem{Github}
        \itemdetails{\href{https://github.com/JohnsonJDDJ}{github.com/JohnsonJDDJ}}
        \shortitem{Personal Website}
        \itemdetails{\href{http://zhihao.myxd.place}{zhihao.myxd.place \\ (for info on all projects)}}
    \section{Skills}
        \shortitem{Languages}
        \itemdetails{
            Python (since 2017)\\%
            SQL (since 2019)\\
            Java (since 2020)\\
            R (since 2020)\\%
            C (since 2021)\\%
            HTML, CSS (since 2017)\\%
        }
        \shortitem{Coursework}
        \itemdetails{
        	    Neural Networks\\%
            Statistical Learning\\%
            Service Operations Design\\%
            Database Systems\\%
            Reproducible Data Science\\%
            General Linear Models\\%
            Data Structures\\%
            Machine Structures\\%
            Linear Algebra\\%
            Probability Theory\\%
        }
        \shortitem{Tools}
        \itemdetails{
            Git (since 2020)\\%
            Jupyter (since 2020)\\%
            MS Azure (since 2022)\\%
            DBeaver (Summer 2021)\\%
            Unix System\\%
            Microsoft Office\\%
        }
\end{minipage}% This hacky percent sign is for removing the space between two columns.
\begin{minipage}[t]{0.77\textwidth}
    \vspace{0.25\baselineskip}
    \section{Education}
    		Note: Applying for master's program with expected graduation date: 05/2024.
        \longitem{University of California, Berkeley}{B.A. Statistics, B.A. Computer Science}{GPA: 3.75/4}{Expected graduation date: 05/2023}
    \section{Experience}
        \longitem{ETL Engineer Intern}{Shanghai DataCVG Co Ltd}{Shanghai, China}{05/2021 - 08/2021}
        \itemdetails{
        Actively contributed to the database services team under the Business Intelligence software company. Engineered directly on the client "FosunPharma"'s pharmaceutical database system by designing and implementing extract-transform-load (ETL) pipelines on relational data:
        \vspace{-0.75\baselineskip}
            \begin{itemize}[itemsep=-4pt]
                \item Collectively designed target relational database architecture with ER diagrams.
                \item Individually wrote queries using DBeaver for the ETL pipeline that combined two source databases.
                \item Debugged architecture failures through long diagnostic process and extensive communication with PM and client representatives.
            \end{itemize}
        }
    \section{Projects}
    		\longitem{Project AEI (Artificial Emotional Intelligence)}{}{Real-time audio emotion classification using neural networks}{01/2022 - Now}
        \itemdetails{
            Advised by Prof. Dacher Keltner, assembled a police aggression discernment and early warning system powered by a parallel CNN Transformer neural network using pytorch. The system is capable to classify emotions from streaming real-life audio speech data:
        \vspace{-0.75\baselineskip}
            \begin{itemize}[itemsep=-4pt]
                \item Trained the parallel network using large emotional databases (RAVDESS, SAVEE) through MS Azure ML cloud compute platform.
                \item Preprocessed streaming audio data into melspectrograms and augmented with Gaussian white noise using pyaudio, librosa and pytorch.
            \end{itemize}
        }
        \longitem{zilean}{}{Python package for data mining and engineering pipelines}{05/2022 - Now}
        \itemdetails{
            Advised by Prof. Fernando Pérez, developed python package "zilean" that bridges the Riot Games API with traditional python ML APIs through implementing customizable data crawler objects and domain specific data manipulator objects.
        \vspace{-0.75\baselineskip}
            \begin{itemize}[itemsep=-4pt]
                \item Designed highly customizable and fully automatic data crawler using rate limiting API request algorithms through requests (python package).
                \item Constructed data mining algorithms incorporating domain specific knowledge for large semi-structured data from the API using native python libraries.
                \item Capable of creating data pipelines producing multidimensional structured data ready for ML or DL tasks. 
                \item Utilizing this tool, predicted League of Legends match outcomes with game statistics before the 16 minute mark by tuning a random forest classifier and a XGBoost classifier through sklearn and hyperopt.
            \end{itemize}
        }
        \longitem{HOYO Lab}{}{Data Modelling in R}{03/2021 - 08/2021}
        \itemdetails{
            Predicted Genshin Impact's damage mechanism by building a basic linear model in R with feature mapping using original data collected through in-game simulations. Displayed the result and hosted an interactive model using R ShinyApp online. Used the model to wrote game tutorials receiving 400,000+ views.
        }
\end{minipage}
\end{document}
